---
title: "Supplemental Materials"
author: Tristan Mahr
output: 
  solarizeddocx::document: default
date: "2025-04-28"
bibliography: notebook/refs.bib
csl: notebook/apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  collapse = TRUE, 
  comment = "#>", 
  fig.height = 3
)

library(tidyverse)
options(width = 72)

source("R/functions.R", keep.source = TRUE)
print_function <- function(f) {
  l <- capture.output(print(f, useSource = TRUE))
  l[1] <- paste0(as.character(substitute(f))," <- ", l[1])
  c(l, "")
}

targets::tar_load(model_stocs_difference_smooth)
v <- list()
v$r <- getRversion()
v$cmdstanr <- utils::packageVersion("cmdstanr")
v$brms <- utils::packageVersion("brms")
v$psych <- utils::packageVersion("psych")
v$mgcv <- utils::packageVersion("mgcv")
v$tidybayes <- utils::packageVersion("tidybayes")
v$ggdist <- utils::packageVersion("ggdist")
v$stan <- model_stocs_difference_smooth$version$cmdstan
```

In this document, we provide and describe the R code used to produce the
main statistical findings of the manuscript.

## Data

Listeners transcribed children's speech, and we measured the children's
intelligibilities. Two different sets or sources of listeners were
compared (in-person versus crowdsourced). Crowdsourced listeners were
presented with an additional set of *fidelity* trials with an adult
speaker so that we could compute *fidelity intelligibility* scores.
These adult speakers should be easy for a reliable listener to
transcribe, so they provide a basis for screening out unreliable
listeners. We consider three different data screening scenarios based on
whether we apply a fidelity criterion of 0 (i.e., no criterion), .8 or
.9. We modeled intelligibility for single-word trials and multiword
trials separately.

Sample values from each column of the dataset are given below:

```{r}
library(tidyverse)
data <- targets::tar_read("data_anon")
glimpse(data)
```

Columns represent the following values:

  - `scenario` - Data-screening scenario: `"screened_at_00"` (no data
    screening), `"screened_at_80"` (at least 80% intelligibility on
    fidelity trials), and `"screened_at_90"` (at least 90%
    intelligibility on fidelity trials)

  - `set`/`o_set` - Listener type: `"in_person"` or `"prolific"`
    (crowdsourced). The `o_set` version is an ordered factor used for
    modeling.

  - `listener` - Random ID for the listener who is transcribing the speech
    samples.
  
  - `listener_order` - Ordering of the listeners (from earliest to
    latest) within listener type and within each child. This ordering
    matters because in each data-screening `scenario`, we select the 
    first 5 listeners that meet a data-screening criterion.

  - `child` - Random ID for the speaker whose speech samples are being
    played and transcribed.

  - `speaker_type` - Speaker type on intelligibility trials:
    `"participant"` for the main intelligibility trials (where the
    speaker is the `child`) or `"adult"` for the fidelity trials used
    for data-screening.

  - `tocs_type` - Intelligibility or speech sample type: `"multiword"`
    for connected speech samples, `"single-word"` for single words, and
    `"overall"` for an average across all trials.

  - `intelligibility`, `intelligibility2`: Average of trial-level
    intelligibilities. For each trial, we compute the intelligibility as
    the proportion of words correctly transcribed on that trials. These
    proportions are then averaged together to produce intelligibility
    scores. `intelligibility2` is `intelligibility` squished into the
    range 0.005--0.995 (for use with beta regression).

  - `sum_m_word`, `sum_s_word`: Total number of words correctly
    transcribed (`sum_m_word`, *matching* words) and total number of
    words in the speech samples (`sum_s_word`, *sample* words). These
    aggregations provide a way to compute a different intelligibility
    measure (proportion of words correctly transcribed), and they are
    used in a logistic regression model for the single-word trials.

  - `age_months`, `age_48`: Age of the `child` in months (`age_months`),
    and a centered age where 48 months has the value 0 (`age_48`). The
    `"adult"` `speaker_type` trials don't have an age associated with
    them.

Each child has 2 in-person listeners and 5 crowdsourced listeners in
each data-screening scenario. We can verify these listener counts.

```{r}
data |> 
  distinct(child, listener, set, scenario) |> 
  count(child, set, scenario, name = "num_listeners") |> 
  count(set, scenario, num_listeners, name = "num_children")
```

We can verify the fidelity intelligibility data screening thresholds in
each group.

```{r}
data |> 
  filter(
    speaker_type == "adult", 
    # average of single-word and connected speech trials
    tocs_type == "overall"
  ) |> 
  group_by(scenario, set) |> 
  summarise(
    min_intell = min(intelligibility),
    n_under_80 = sum(intelligibility < .80),
    n_under_90 = sum(intelligibility < .90),
    .groups = "drop"
  )
```


(These counts slightly differ from a table in the manuscript because
that table includes an additional 3 exclusions where an excluded
listener's first replacement also had to be excluded but here we
just count the first 5 listeners that satisfy inclusions.)

### Intraclass correlation

We report the intraclass correlation statistic as a measure of
interrater reliability. We deferred ICC calculation to the psych package
[vers. `r v$psych`, @r-psych]. `pysch::ICC()` requires the data to have one
column per "judge" and no grouping variables, so we use `unstack()` (a
no-frills `pivot_wider()`) in each `set` × `scenario` × `tocs_type`
subgroup, compute the ICCs and extract the relevant values. 

```{r}
data |> 
  filter(speaker_type == "participant", tocs_type != "overall") |>
  # Number the listeners within each child and each subsample
  group_by(set, scenario, tocs_type, child) |> 
  mutate(
    listener_number = seq_along(listener)
  ) |> 
  ungroup() |> 
  # Compute ICCs in each subsample
  group_by(set, scenario, tocs_type) |> 
  reframe(
    datasets = pick(c(listener_number, intelligibility)) |> 
      unstack(intelligibility ~ listener_number) |> 
      list(),
    iccs = datasets |> 
      lapply(psych::ICC, lmer = FALSE) |> 
      lapply(getElement, "results")
  ) |> 
  unnest(iccs) |> 
  filter(type %in% c("ICC2", "ICC2k")) |> 
  select(-F, -p, -df1, -df2, -datasets) |>
  mutate(
    set = set |> printy::str_replace_same_as_previous(""),
    scenario = scenario |> printy::str_replace_same_as_previous(""),
    tocs_type = tocs_type |> printy::str_replace_same_as_previous(""),
  ) |> 
  rename(ll = `lower bound`, ul = `upper bound`) |> 
  print(n = Inf)
```


## Bayesian generalized additive mixed models

We fit a pair of Bayesian regression models with brms: one for connected speech
intelligibility and one for single-word intelligibility. We regressed 
intelligibility onto age and listener type with by-child random effects of 
listener type. We only examined `"participant"` intelligibility scores (the 
fidelity trials were only used for data-screening). These models had repeated 
measures with 1 intelligibility score per listener and 2 or 5 
listeners per child.

The same basic regression setup was used to fit each model, so we describe the 
first model in more detail.

### Connected speech model

We used beta regression for the connected speech model. brms uses the
mean-precision ($\mu, \phi$) parameterization of the beta distribution
where the mean is a proportion and the precision is a positive number.
We used the default link functions: logit for the mean (so the model for
the mean works on the log-odds scale) and log for the precision.




```{r}
targets::tar_load("model_stocs_difference_smooth")
model_stocs_difference_smooth |> 
  family() |> 
  _[c("family", "dpars", "link", "link_phi")] |> 
  str()
```

Beta regression does not allow proportions of 0 or 1, so these 
floor and ceiling values were squished into the range 0.005 and .995.

```{r}
y <- model_stocs_difference_smooth$data$intelligibility2
range(y)
sum(y == .005)
sum(y == .995)
```

The regression model in brms syntax is given below:

```{r}
formula(model_stocs_difference_smooth)
```

For the mean model, we have a parametric effect of listener type (`set`)
and by-child random effects of listener type (`(set | child)`). We also
have a thin-plate spline smooth of age (`s(age_48)`) and a *difference
smooth* of age for the two listener types. Supplying an ordered factor
(`o_set`) causes mgcv/brms to compute a difference smooth.

Below we plot the baseline smooth (in-person listeners) and the
difference smooth (in-person minus crowdsourced listeners). There is not
a clear difference in the effects of age on intelligibility in the
smooths between the two listener groups (on the logit scale):

```{r}
library(ggplot2)
library(patchwork)

cs1 <- model_stocs_difference_smooth |> 
  brms::conditional_smooths("s(age_48)") |> 
  # i.e., return the plot object but don't display it
  plot(plot = FALSE)

cs2 <- model_stocs_difference_smooth |> 
  brms::conditional_smooths(
    "s(age_48, by = o_set)", 
    int_conditions = list(o_set = "prolific")
  ) |> 
  plot(plot = FALSE)

cs1[[1]] + ylim(-2.75, 2.75) + cs2[[1]] + ylim(-2.75, 2.75)
```

#### Marginal means

Our visualizations used marginal means from each model. That is, a mixed
effects model's fixed effects estimates a conditional mean: It
is the expected intelligibility score for a participant whose random
effect values have all been set to 0. This conditional mean is not the
same as the *marginal* or population mean, so we have take additional
steps to compute this marginal mean. Namely, we simulate new children
based on the model (sample new random effect values) and then average
(or *marginalize*) over them.

We used the following recipe to compute marginal means. 

```{r, include = FALSE}
l1 <- print_function(compute_tocs_marginal_means)
```
```{r}
# 0. Prepare a prediction grid for a new out-of-sample participant
newdata <- targets::tar_read(newdata_stocs)

```
```{r, code = l1}
```


Because of the long computation time, we instead read in and preview a 
precomputed copy of the marginal means. 

```{r}
data_stocs_marginal_means <- targets::tar_read(data_stocs_marginal_means)
data_stocs_marginal_means
```

From these conditional means, it is straightforward to compute growth 
curves presented in the manuscript:

```{r}
ggplot(data_stocs_marginal_means) + 
  aes(x = age_48, y = .marginal) +
  ggdist::stat_lineribbon(
    aes(group = set, fill = set), 
    .width = .95,
    alpha = .5
  )
```



#### Effect of intelligibility on listener type difference

For the plot of the in-person listener advantage versus in-person
intelligibility, we fix the in-person intelligibility to a narrow range
of values (i.e., we bin them) and gather all of the intelligibility
difference scores for that range of values.

For example, here are all the rows in the marginal means dataframe where the 
in-person marginal means that are binned to .65. 

```{r}
d <- data_stocs_marginal_means |> 
  select(-.conditional) |> 
  filter(set != "prolific") |> 
  tidyr::pivot_wider(names_from = set, values_from = .marginal) |> 
  ungroup()

d_at_65 <- d |> 
  mutate(
    in_person = plyr::round_any(in_person, .025)
  ) |> 
  filter(in_person == .65)

d_at_65
```

There are `r nrow(d_at_65)` ages × posterior draws where the marginal mean
is binned to this value. These include predictions from different ages and
different amounts of listener type differences (`diff`). We can look at the
distribution of these listener type differences.

```{r}
hist(d_at_65$diff)
```

This distribution, for each difference, are presented in the manuscript. We
used the general recipe given below. The main details are that the differences
1) we exclude any bins with fewer than 200 posterior draws and 2) within each
bin the differences within a posterior draw are averaged together. 

```{r}
# Bin the in-person scores and count the differences in each bin. Discard 
# any bin with fewer than 200 posterior total draws.
d_intervals <- d |> 
  mutate(
    in_person = plyr::round_any(in_person, .025)
  ) |> 
  group_by(outcome, level, in_person) |> 
  mutate(n_draws = n()) |> 
  ungroup() |> 
  filter(n_draws > 200) |> 
  # If a posterior draw hits an in-person intelligibility bin multiple
  # times, because a curve plateaus or horseshoes, take the average
  # of the differences for each draw. Now each posterior draw
  # can only have one vote.
  group_by(outcome, level, in_person, .draw) |> 
  summarise(
    diff = mean(diff),
    .group = "drop"
  ) |> 
  # For each in-person intelligibility bin, get median and 95% interval.
  group_by(outcome, level, in_person) |> 
  ggdist::median_qi(diff)

d_intervals

ggplot(d_intervals) + 
  aes(x = in_person) + 
  geom_ribbon(aes(ymin = .lower, ymax = .upper), alpha = .2) +
  geom_line(aes(y = diff))
```



## Single-word intelligibility

The single-word intelligibility model was completely analogous to the multiword 
model except that it was used logistic regression model (a binomial family 
with logit link).

```{r}
targets::tar_load("model_wtocs_difference_smooth")
model_wtocs_difference_smooth |> 
  family() |> 
  _[c("family", "dpars", "link")] |> 
  str()
```

The binomial family estimates a number of successes in a number of trials. The
brms `trials()` syntax capture those values in the lefthand side of the
regression formula:

```{r}
formula(model_wtocs_difference_smooth)
```

Recall that `sum_m_word` is the total number of words correctly
transcribed by a listener and `sum_s_word` is the total number of words
presented to the listener.

This model also used a difference smooth, and we can visualize the two smooths
as we did above.

```{r}
cs1 <- model_wtocs_difference_smooth |> 
  brms::conditional_smooths("s(age_48)") |> 
  # i.e., return the plot object but don't display it
  plot(plot = FALSE)

cs2 <- model_wtocs_difference_smooth |> 
  brms::conditional_smooths(
    "s(age_48, by = o_set)", 
    int_conditions = list(o_set = "prolific")
  ) |> 
  plot(plot = FALSE)

cs1[[1]] + ylim(-2.75, 2.75) + cs2[[1]] + ylim(-2.75, 2.75)
```

The marginal means computation and differences-by-in-person-intelligibility 
computation used the same recipes (and code) as outlined above.


## Model comparisons

Do we need the difference smooth in each of these models? The right
panel of the marginal smooths mostly shows a horizontal line hovering
around 0, suggesting a limited difference. Model comparison with
approximate leave-one-out (LOO) techniques [@loo], on the other hand, does not
strongly favor the simpler shared smooth model over the model with a 
baseline smooth and difference smooth. 

```{r}
targets::tar_load(model_stocs_difference_smooth)
targets::tar_load(model_stocs_shared_smooth)
targets::tar_load(model_wtocs_difference_smooth)
targets::tar_load(model_wtocs_shared_smooth)

brms::loo_compare(
  model_wtocs_shared_smooth, 
  model_wtocs_difference_smooth
) |> 
  print(simplify = FALSE) 

brms::loo_compare(
  model_stocs_shared_smooth, 
  model_stocs_difference_smooth
) |> 
  print(simplify = FALSE) 
```

We interpret this output by looking at `elpd_loo` (expected log
predictive density). Higher values indicate better expected predictive
performance on out of sample data. The difference in ELPD between each
model and the highest ELPD model (i.e., first row) is given in
`elpd_diff`. We need to interpret these differences in light of the
standard error `se_diff`. Neither of the differences reported above is
greater than 2-SEs in magnitude, so there is not a statistically clear
difference between the models in terms of predictive performance.

We also note that leave-one-out comparison is not ideal for
repeated-measures data but leave-one-group-out techniques are
computationally prohibitive.


## Sampling details

Hamilitonian Monte Carlo sampling diagnostics indicated no major issues. There
were no divergent transitions, the max treedepth on the iterations did not reach
the treedepth limit, and the so-called estimated fraction of missing information
statistic was greater than .3 on every chain.

```{r}
get_hmc_details <- function(model, ...) {
  df <- brms::nuts_params(model, ...)
  df$model <- as.character(substitute(model))
  df$limit_treedepth <- model$stan_args$control$max_treedepth %||% 10
  tidyr::pivot_wider(
    data = df,
    names_from = "Parameter", 
    values_from = "Value"
  )
}

bind_rows(
  get_hmc_details(model_stocs_difference_smooth),
  get_hmc_details(model_wtocs_difference_smooth)
) |> 
  group_by(model, chain = Chain) |> 
  summarise(
    n_draws = n(),
    efmi = mean(diff(energy__) ^ 2) / var(energy__),
    n_divergent = sum(divergent__),
    max_depth = max(treedepth__),
    limit_depth = unique(limit_treedepth),
    .groups = "drop"
  )
```

The Rhat and effective sample size statistics were also satisfactory
(Rhats \<= 1.01, ESS \> 100 per chain, or 400):

```{r}
get_convergence_stats <- function(model) {
  df <- posterior::summarise_draws(
    model, 
    posterior::default_convergence_measures()
  )
  df$model <- as.character(substitute(model))
  df
}

bind_rows(
  get_convergence_stats(model_stocs_difference_smooth),
  get_convergence_stats(model_wtocs_difference_smooth)
) |> 
  group_by(model) |> 
  summarise(
    model = "model_stocs_difference_smooth",
    max_rhat = max(rhat), 
    min_ess_bulk = min(ess_bulk),
    min_ess_tail = min(ess_tail)
  )
```



## Prior description

Because these models estimate means on the logit scale, we used weakly
informative priors of Normal(0, 1) for the regression coefficients and standard
deviations of the random effects. Because mgcv transforms a spline
basis to absorb constraints and penalty terms in sophisticated ways, appropriate
scale values for the smooth terms are not clear a priori. Therefore, we used
wider Normal(0, 2) priors for the SDs of the smoothing coefficients.

We used a weakly informative LKJ(2) prior on the correlations in the random-effect 
matrix. This prior pulls probability mass away from boundary correlations 
(1 or −1).

For the beta regression model, we also estimated a phi parameter with a
log link function and as a result, the effect of age on the precision on
the outcome scale is multiplicative. Therefore, we used a weakly
informative Normal(0, 2) prior.

Any other unspecified priors used brms defaults.

```{r}
model_stocs_difference_smooth$prior

model_wtocs_difference_smooth$prior 
```

## Software details

Analyses were conducted in the R programming language [vers. `r v$r`,
@r-base]. Models were fit using the Stan programming language
[vers. `r v$stan`,@stan-base] via the brms
[vers. `r v$brms`,@r-brms] and cmdstanr [vers. `r v$cmdstanr`,
@r-cmdstanr] R packages. The implementation of smoothing splines relies
on mgcv [vers. `r v$mgcv`, @mgcv-book]. Handling the posterior samples
was greatly simplified by tidybayes [vers. `r v$tidybayes`,
@r-tidybayes] and ggdist [vers. `r v$ggdist`, @ggdist].

Because we rely on reading in cached models, it's important to ask
the models for their software versions as well:

```{r}
model_stocs_difference_smooth$version |> 
  lapply(as.character) |> 
  str()

model_wtocs_difference_smooth$version |> 
  lapply(as.character) |> 
  str()
```



## Full Model Summaries

For completeness, here are the full model summaries, but note that these
are generalized linear models with nonlinear link functions so it is
difficulty to interpret individual coefficients in isolation. Note also
that the quantities for the smoothing spline SDs and linear effects from
each smooth are generally uninterpretable because of several matrix
transformations. Thus, these models are best understood through the
expectations or predictions computed from them.

Multiword intelligibility:

```{r}
summary(model_stocs_difference_smooth, priors = TRUE)
```

Single word intelligibility:

```{r}
summary(model_wtocs_difference_smooth, priors = TRUE)
```

## Modeling functions

The following code block shows the modeling workflow we used to fit
these models. Each family of models has a single function. A user passes
in a dataset, a model `flavor`, an optional random number seed and
optional `tag`. The `flavor` is used to look up the appropriate model
formula, and the `tag` is used to differentiate two models with
different datasets but the same flavor.

```{r, include = FALSE}
source("R/functions.R", keep.source = TRUE)
print_function <- function(f) {
  l <- capture.output(print(f, useSource = TRUE))
  l[1] <- paste0(as.character(substitute(f))," <- ", l[1])
  c(l, "")
}

l <- c(
  print_function(fit_stocs_model), 
  print_function(fit_wtocs_model),
  print_function(lookup_brms_priors),
  print_function(has_random_slope_correlation),
  print_function(add_loo_criterion),
  print_function(brm_args)
)
```

```{r, code = l}
```



## References

